\chapter{Experimental Results} 
\label{ch:experimentalresults}

To evaluate the success of the composer, it seemed most appropriate to have a user experience study.  It would not be a fair test of how effective the tool is at helping a person compose if the only people that were to test the tool have high level music and computer science knowledge.  To truly understand how the tool performs, it needed to be placed in the hands of a general audience.

\vspace{\baselineskip}

When designing software, two of the key elements are the user interface (UI) and user experience (UX).  The UX is how the user feels about and responds to a product.  It is based on how the tool is presented, acquired, and how it functions.  This chapter of the document details the design of the UX study, its evaluation, and any potential threats to its validity.

\section{User Experience Study}
\label{sec:userexperiencestudy}

As a part of this study, there are several important metrics that had to be gauged in order to determine the effectiveness of the tool.  These include:

\begin{itemize}
	\item User Background
	\item System Availability
	\item System Performance
	\item System Accessibility
	\item User Impressions
\end{itemize}

Several questions were presented to the user about specific areas within each of these larger categories.  This data was then used to determine the performance in the category as a whole.  The specific categories, subcategories, and related questions are listed below.

\subsection{User Background}
\label{subsec:userbackground}

This sections asks the user some demographic questions related to the user's previous experience and gets important connecting information.

\subsubsection{Music Background}
\label{subsubsec:musicbackground}

Rate your amount of music theory knowledge.

\begin{itemize}
	\item No Knowledge
	\item Beginner
	\item Intermediate
	\item Advanced
	\item Expert
\end{itemize}

\noindent Rate your ability to read music.

\begin{itemize}
	\item No Knowledge
	\item Beginner
	\item Intermediate
	\item Advanced
	\item Expert
\end{itemize}

\noindent Rate your knowledge related to instrumental and/or vocal performance.

\begin{itemize}
	\item No Knowledge
	\item Beginner
	\item Intermediate
	\item Advanced
	\item Expert
\end{itemize}

\noindent Have you had musical instruction?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\noindent If yes, please select all of the following types that apply.

\begin{itemize}
	\item Instrumental Instruction
	\item Vocal Instruction
	\item Theory Instruction
	\item History Instruction
	\item Composition Instruction
\end{itemize}

\noindent Have you written/composed music in the past?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\subsubsection{Computer Science Background}
\label{subsubsec:computersciencebackground}

Rate your amount of computer science knowledge.

\begin{itemize}
	\item No Knowledge
	\item Beginner
	\item Intermediate
	\item Advanced
	\item Expert
\end{itemize}

\noindent Have you had some form of computer science instruction?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\noindent If yes, please select all of the following types that apply.

\begin{itemize}
	\item Self Taught
	\item Online Instruction
	\item Classroom Instruction
	\item Professional Instruction
\end{itemize}

\subsubsection{Composition Analysis}
\label{subsubsec:compositionanalysis}

Would you like to submit your compositions for analysis?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\noindent If yes, would you like to be listed as the composer?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\noindent If yes, please provide how you wish to be named.

\subsection{System Availability}
\label{subsec:systemavailability}

This particular metric deals with whether or not the user was able to access the site and on what sort of device and conditions they had when the attempted to access the site.

\subsubsection{General Access}
\label{subsubsec:generalaccess}

Were you able to access and use the site?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\vspace{\baselineskip}

\noindent Did you try on more than one occasion?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\subsubsection{Platform}
\label{subsubsec:platform}

On what sort of device did you try to use the site?

\begin{itemize}
	\item Desktop Computer
	\item Laptop
	\item Tablet
	\item Mobile Phone
	\item Other
\end{itemize}

\subsubsection{Operating System}
\label{subsubsec:operatingsystem}

What operating system do you have on your device?

\begin{itemize}
	\item Windows
	\item macOS
	\item iOS
	\item Linux
	\item Android
	\item Other
\end{itemize}

\subsubsection{Browser}
\label{subsubsec:browser}

What web browser were you using?

\begin{itemize}
	\item Chrome
	\item Safari
	\item Internet Explorer
	\item Microsoft Edge
	\item Firefox
	\item Other
\end{itemize}

\subsection{System Performance}
\label{subsec:systemperformance}

This metric deals with how quickly and completely the system responded to the user.

\subsubsection{Load Time}
\label{subsubsec:loadtime}

Did each of the pages load quickly?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\noindent If no, with which page(s) did the issue occur?

\subsubsection{Analysis Speed}
\label{subsubsec:analysisspeed}

Were the analysis, notation, and playback returned quickly?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\subsubsection{Rendering Issues}
\label{subsubsec:renderingissues}

Was there any part of the page that was missing?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\noindent If yes, with which page(s) did the issue occur?

\subsection{System Accessibility}
\label{subsec:systemaccessibility}

This metric deals with the elements of the UI.

\subsubsection{Layout}
\label{subsubsec:layout}

Does the layout of the pages make sense to you?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\noindent If no, with which element(s) did you have an issue?

\subsubsection{Design}
\label{subsubsec:design}

Does the overall design of the page and the elements make sense to you?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\noindent If no, which which item(s) did you have an issue?

\subsubsection{Sizing}
\label{subsubsec:Sizing}

Was everything on the page sized appropriately to make it easy to use?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\noindent If no, which which element(s) did you have an issue?

\subsection{User Impressions}
\label{subsec:userimpressions}

This sections determines the user's progress though the tool and their overall comments about using it.

\subsubsection{Completion}
\label{subsubsec:completion}

Were you able to go through the entire composition process?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\noindent If no, where did you stop?

\noindent Why did you stop?

\subsubsection{Frustrations}
\label{subsubsec:Frustrations}

Was there any part of using this tool that was frustrating or upsetting?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\noindent If yes, with what part(s) of the tool did you experience this with?

\subsubsection{Changes}
\label{subsubsec:Changes}

Are there any changes that you would make to this tool?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\noindent If yes, what are they?

\subsubsection{Comments}
\label{subsubsec:Comments}

What other comments do you have for the developer of this tool?

\section{Study Evaluation}
\label{sec:studyevaluation}



\section{Threats to Validity}
\label{sec:threatstovalidity}

