\unnumberedchapter{Appendix} 
\chapter*{Appendix}
\label{ch:appendix}

\noindent In order to evaluate this tool as part of a user experience study, it would be necessary to gauge the following metrics:

\begin{itemize}
	\item User Background
	\item System Availability
	\item System Performance
	\item System Accessibility
	\item User Impressions
\end{itemize}

The following is the list of questions that would be used for the listed metrics:

\noindent Rate your amount of music theory knowledge.

\begin{itemize}
	\item No Knowledge
	\item Beginner
	\item Intermediate
	\item Advanced
	\item Expert
\end{itemize}

\noindent Rate your ability to read music.

\begin{itemize}
	\item No Knowledge
	\item Beginner
	\item Intermediate
	\item Advanced
	\item Expert
\end{itemize}

\noindent Rate your knowledge related to instrumental and/or vocal performance.

\begin{itemize}
	\item No Knowledge
	\item Beginner
	\item Intermediate
	\item Advanced
	\item Expert
\end{itemize}

\noindent Have you had musical instruction?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\noindent If yes, please select all of the following types that apply.

\begin{itemize}
	\item Instrumental Instruction
	\item Vocal Instruction
	\item Theory Instruction
	\item History Instruction
	\item Composition Instruction
\end{itemize}

\noindent Have you written/composed music in the past?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\noindent Rate your amount of computer science knowledge.

\begin{itemize}
	\item No Knowledge
	\item Beginner
	\item Intermediate
	\item Advanced
	\item Expert
\end{itemize}

\noindent Have you had some form of computer science instruction?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\noindent If yes, please select all of the following types that apply.

\begin{itemize}
	\item Self Taught
	\item Online Instruction
	\item Classroom Instruction
	\item Professional Instruction
\end{itemize}

\noindent Would you like to submit your compositions for analysis?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\noindent If yes, would you like to be listed as the composer?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\noindent If yes, please provide how you wish to be named.

\vspace{\baselineskip}

\noindent Were you able to access and use the site?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\noindent Did you try on more than one occasion?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\noindent On what sort of device did you try to use the site?

\begin{itemize}
	\item Desktop Computer
	\item Laptop
	\item Tablet
	\item Mobile Phone
	\item Other
\end{itemize}

\noindent What operating system do you have on your device?

\begin{itemize}
	\item Windows
	\item macOS
	\item iOS
	\item Linux
	\item Android
	\item Other
\end{itemize}

\noindent What web browser were you using?

\begin{itemize}
	\item Chrome
	\item Safari
	\item Internet Explorer
	\item Microsoft Edge
	\item Firefox
	\item Other
\end{itemize}

\noindent Did each of the pages load quickly?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\noindent If no, with which page(s) did the issue occur?

\vspace{\baselineskip}

\noindent Were the analysis, notation, and playback returned quickly?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\noindent Was there any part of the page that was missing?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\noindent If yes, with which page(s) did the issue occur?

\vspace{\baselineskip}

\noindent Does the layout of the pages make sense to you?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\noindent If no, with which element(s) did you have an issue?

\vspace{\baselineskip}

\noindent Does the overall design of the page and the elements make sense to you?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\noindent If no, which which item(s) did you have an issue?

\vspace{\baselineskip}

\noindent Was everything on the page sized appropriately to make it easy to use?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\noindent If no, which which element(s) did you have an issue?

\vspace{\baselineskip}

\noindent Were you able to go through the entire composition process?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\noindent If no, where did you stop?

\vspace{\baselineskip}

\noindent Why did you stop?

\vspace{\baselineskip}

\noindent Was there any part of using this tool that was frustrating or upsetting?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\noindent If yes, with what part(s) of the tool did you experience this with?

\vspace{\baselineskip}

\noindent Are there any changes that you would make to this tool?

\begin{itemize}
	\item Yes
	\item No
\end{itemize}

\noindent If yes, what are they?

\vspace{\baselineskip}

\noindent What other comments do you have for the developer of this tool?